\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-06-11 paper.qmd
langevitour figure caption

```{r}
#| label: fig-hex-param
#| fig-cap: "Illustration of the components of the hexagon grid showing the notation used in explanations."
#| out-height: 30%
#| fig-width: 3
#| fig-height: 4.5
#| fig-pos: H

@@

Screen shots of the **langevitour** of the S-curve, shows the model-in-data space, a video of the tour animation is available at (<https://youtu.be/G1m4q9k--v4>).
:::

>>>>

```{r}
#| label: fig-hex-param
#| fig-cap: "Illustration of the components of the hexagon grid with notation."
#| out-height: 30%
#| fig-width: 3
#| fig-height: 4.5
#| fig-pos: H

@@

Projections of the $7\text{-}D$ S-curve data (purple points) overlaid with the model (black grid with  green points indicating bin means) constructed from the UMAP layout, with XXX bins (using the **langevitour** software). The model closely fits the shape of this data. A video of the full tour is available at (<https://youtu.be/G1m4q9k--v4>).
:::

### 2024-06-11 paper.tex
langevitour figure caption

\caption{\label{fig-hex-param}Illustration of the components of the
hexagon grid showing the notation used in explanations.}

@@

\caption{\label{fig-scurve-sc}Screen shots of the \textbf{langevitour}
of the S-curve, shows the model-in-data space, a video of the tour
animation is available at (\url{https://youtu.be/G1m4q9k--v4}).}

>>>>

\caption{\label{fig-hex-param}Illustration of the components of the
hexagon grid with notation.}

@@

\caption{\label{fig-scurve-sc}Projections of the \(7\text{-}D\) S-curve
data (purple points) overlaid with the model (black grid with green
points indicating bin means) constructed from the UMAP layout, with XXX
bins (using the \textbf{langevitour} software). The model closely fits
the shape of this data. A video of the full tour is available at
(\url{https://youtu.be/G1m4q9k--v4}).}
